This is a title

### 2021-05-21 manuscript/ms.tex
theory updates from may 21; need to re-think eqns 9-10 (kinetic energy equation?)

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}

@@

\section{Theory}
\label{sec:theory}
Throughout this work, we will utilize a modified version of the Boussinesq equations of motion, similar to the model derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In dimensional form,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho'}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho'}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
In this model, $\rho_0$ is a (constant) background density and $\rho'$ are fluctuations which act only in the buoyancy force and varies linearly with the temperature $T$ according to the coefficient of thermal expansion, $\alpha = \partial\ln\rho / \partial T$.
Furthermore, $\vec{u}$ is the velocity vector, $\nu$ and $\chi$ are respectively the viscous and thermal diffusivity, $Q$ is a bulk internal heating term \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and $\gradad$ is the adiabatic temperature gradient (we define $\gradad$ as a positive value to align with stellar structure conventions; this means marginal stability is achieved when $\partial_z T = -\gradad$).
We modify the model of \citet{spiegel_veronis_1960} to allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
We assume that the classical thermal diffusion term $\chi \grad^2 T'$  only acts on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$.

The basis of the theory of \citet{zahn1991} is that the size of the convection zone is determined by the horizontally-averaged energetics and buoyancy breaking.
We assume convection reaches a time-stationary, equilibrium state; we vertically integrate Eqn.~\ref{eqn:temperature} and take a horizontal average to find
\begin{equation}
\Ftot = \Frad + \Fconv = \int Q dz + \Fbot,
\end{equation}
with $\Fconv = \overline{w T}$ and $\Fbot$ the flux at the bottom of the convective domain and $\Ftot$ the total flux, which can vary in height according to integral of $Q$.
We next assume that convection penetrates above the nominal schwarzschild boundary of the convection zone and mixes the temperature gradient towards the adiabatic in that region.
Thus, in that region, the convective flux can be found,
\begin{equation}
\Fconv = \Ftot - F_{\rm{rad, ad}} = \Ftot - k \grad_{\rm{ad}}.
\end{equation}
By definition, in this region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, where $\grad_{\rm{rad}} = \Ftot/k$, so this requires that $\Fconv < 0$ in the convective penetration region.
We next assume that the temperature and velocity are highly correlated in the penetrative region with very similar horizontal fluctuations,
\begin{equation}
w(x,y,z) = W(z)h(x,y),
\qquad
T'(x,y,z) = \delta T(z)h(x,y).
\end{equation}
We here assume that $\overline{h} = 0$ and $\overline{h^2} \neq 0$.
We can then express the convective flux in terms of these vertically-varying profiles and an average over the horizontal structure of the flows,
\begin{equation}
\Fconv \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
\label{eqn:Fconv_vertical}
\end{equation}
In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must be oppositely signed and the convective flows should eventually come to a stop through buoyancy breaking.
This is achieved through a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
\begin{equation}
\frac{1}{2}\frac{d w^2}{dz} = |\alpha| g T'.
\end{equation}
Multiplying both sides by $h(x,y)$, taking a horizontal average, and then substituting $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation,
\begin{equation}
\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 = \Fconv dz.
\label{eqn:theory_ode}
\end{equation}
This equation can be integrated over the depth of the convection zone from $W = 0$ to $W = W_0$ at the convective boundary, as well as over the penetration zone from $W = W_0$ to where $W = 0$.
We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
Integrating Eqn.~\ref{eqn:theory_ode} over the CZ and PZ and taking a ratio of these two equations, we find
\begin{equation}
-\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}} = 
\frac{\int_{\rm{PZ}} \Fconv dz}{\int_{\rm{CZ}} \Fconv dz}.
\label{eqn:theory_fraction}
\end{equation}
In order to move further with this theory, it is necessary to specify the vertical shape of $\Fconv$, which is in turn set by $Q$, $\gradad$, and $k$.
We will assume that $\gradad$ has a constant value and that the internal heating $Q$ is localized near the bottom of the CZ so that a constant convective flux $\Fcz$ is carried in the bulk convection zone.
As a result, the vertical profile of $\Frad$ and $\Fconv$ is determined completely by the behavior of $k(z)$ near the convective boundary.
We will study two cases in this work: a discontinuous jump in $k(z)$ at the convective boundary, and a piecewise-linear profile of $k(z)$ whose derivative may be discontinuous at the convective boundary.

\subsection{Case I: Discontinuous radiative conductivity}
\label{sec:discontinuous_theory}
We first consider a radiative conductivity $k(z)$ which is discontinuous, with a value of $k_{\rm{CZ}}$ in the convection zone and larger value $k_{\rm{RZ}}$ in the PZ and radiative zone (RZ).
The values of $k$ are chosen so that the convective flux follows
\begin{equation}
\Fconv(z) = \begin{cases}
\Fcz			&	z \leq \Lcz,\\
-\mP_D^{-1} \Fcz & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\mP_D^{-1}$ is the ``penetration parameter'' (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = \Lcz$ and the penetration zone from $z = \Lcz$ to $z = \Lcz + \dP$,
\begin{equation}
\frac{\dP}{\Lcz} = \mP_D
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}.
\label{eqn:discontinuous_prediction}
\end{equation}
We then see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the horizontal structure of the convective dynamics in the PZ and the CZ.
This makes sense; As $\mP_D$ grows, the magnitude of $\Fconv$ in the PZ shrinks, and so too does the breaking force of buoyancy.

\subsection{Case II: Piecewise linear radiative conductivity}
\label{sec:linear_theory}
We next assume that $k(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be.
As a result, the convective flux in the vicinity of the boundary takes the form
\begin{equation}
\Fconv(z) = 
\begin{cases}
(\partial_z k)_{\rm{cz}}\gradad (\Lcz - z) & z \leq \Lcz \\
-\mP_L^{-1}(\partial_z k)_{\rm{cz}}\gradad (z - \Lcz) & z > \Lcz
\end{cases},
\end{equation}
where we assume that $(\partial_z \Frad)_{\rm{cz}} =  (\partial_z k)_{\rm{cz}}\gradad$ is a constant.
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\dP}{\Lcz} = \sqrt{\mP_L
\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
In this work, we will test the predictions of Eqns.~\ref{eqn:linear_prediction} and \ref{eqn:discontinuous_prediction}.
Our aim is to see if the predicted scalings with $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\frac{(\overline{h}^3/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}}$ in local simulations.

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the convection zone, the timescale of freefall across that convection zone, and the temperature scale of the internal heating over that freefall time,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau T,\qquad
\partial_{t^*} = \tau^{-1}\partial_t = \left(\frac{\alpha g Q_0}{\Lcz}\right)^{1/3} \partial_t,\qquad
\grad^* = \Lcz^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 \Lcz^2\right)^{1/3}\vec{u},
\\
&k^* = (\Lcz^2 \tau^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} \Lcz}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
Here, quantities with $*$ (e.g., $T^*$) refer to the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}, and going forward quantities without these (e.g., $T$) will be dimensionless.
The equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain contains at least two convection zone length scales according to the Schwarzschild criterion.
We decompose the temperature field into a background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

@@

In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency $f_{\rm{conv}} \approx \angles{\vec{u}} \Lcz \approx 1$.
We want to allow the stiffness of the radiative-convective interface to be a control parameter.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}} \approx N^2,
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $T_0$ which in turn sets the value of $k$ in the radiative zone.

The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, which determines the size of the convective penetration region.
We define
\begin{equation}
\mP = -\frac{\Fconv|_{\rm{CZ}}}{\Fconv|_{PZ}},
\end{equation}
where $\Fconv|_{PZ}$ is the negative convective flux carried in a perfectly adiabatic convective penetration region.
We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$.

Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
The value of $\mR$ roughly corresponds to the value of the peak Reynolds number measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
Astrophysical convection is in the limit of $\Pran \ll 1$; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.

\subsection{Case I: Discontinuous radiative conductivity}
Most of the simulations in this paper study simulations with a discontinuous radiative conductivity,
\begin{equation}
k_D(z) = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases}.
\label{eqn:sim_discontinuous_k}
\end{equation}
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry the $\Fbot$ at $z = 0$ and that the radiative gradient can carry the flux for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

@@

\subsection{Case II: Piecewise linear radiative conductivity}
We additionally study a select few simulations where the radiative conductivity's gradient is piecewise discontinuous,
\begin{equation}
\partial_z k = \partial_z k_0
\begin{cases}
1	&	z < 1 \\
\mP_L^{-1} &	z \geq 1
\end{cases}
\label{eqn:sim_linear_k}
\end{equation}
Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
by this choice, we require
\begin{equation}
\partial_z k_0 = \frac{\delta_H}{\Lcz \mS \xi},\qquad
k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
\gradad = Q \mS \xi,
\end{equation}
where $\xi \equiv 1 + \mP_L(1 + \zeta)$.
In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
As in section \ref{sec:linear_theory}, we expect $\delta_p \propto \mP_L^{1/2}$.

@@

>>>>

%%%% Custom commands
\newcommand{\gradrad}{\ensuremath{\nabla_{\rm{rad}}}}
\newcommand{\gradad}{\ensuremath{\nabla_{\rm{ad}}}}
\newcommand{\delp}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Fbot}{\ensuremath{F_{\rm{bot}}}}
\newcommand{\Ftot}{\ensuremath{F_{\rm{tot}}}}
\newcommand{\Frad}{\ensuremath{F_{\rm{rad}}}}
\newcommand{\Fconv}{\ensuremath{F_{\rm{conv}}}}
\newcommand{\Fcz}{\ensuremath{F_{\rm{cz}}}}
\newcommand{\mP}{\ensuremath{\mathcal{P}}}
\newcommand{\mD}{\ensuremath{\mathcal{D}}}
\newcommand{\dP}{\ensuremath{\delta_{\rm{p}}}}
\newcommand{\Lcz}{\ensuremath{L_{\rm{cz}}}}
\newcommand{\mR}{\ensuremath{\mathcal{R}}}
\newcommand{\mS}{\ensuremath{\mathcal{S}}}
\newcommand\Pran{\ensuremath{\mathrm{Pr}}}
\newcommand{\brunt}{Brunt-V\"{a}is\"{a}l\"{a}}

@@

\section{Theory}
\label{sec:theory}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a (constant) background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[as in e.g.,][]{goluskin_vanderpoel_2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
These equations are similar to those derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}, but we allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
The classic Boussinesq thermal diffusion term $\chi \grad^2 T'$ therefore carries no flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and primes ($'$) represent fluctuations away from those horizontal means.
Throughout this work, we will consider Cartesian coordinates $(x, y, z)$, but this analysis is generalizeable to spherical geometry.
We will furthermore assume a model in which an unstable convection zone sits below a stable radiative zone, but this analysis also holds for the inverted problem.

\citet{zahn1991} theorized that the size of the convection zone is determined by the horizontally-averaged energy fluxes.
Assuming convection reaches a time-stationary state, we horizontally-average the vertically integrated Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\end{equation}
where $\overline{\Fconv} = \overline{w T}$, is $\Fbot$ the flux carried at the bottom of the considered domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We next assume that convection penetrates above the Schwarzschild boundary of the convection zone at $z = L_s$ and mixes the temperature gradient to the adiabatic in the region $z \in [L_s, L_s + \delp]$, where $\delp$ is the penetration depth.
This assumption specifies the convective flux in the penetrative region,
\begin{equation}
\overline{\Fconv}(z \in [L_s, L_s + \delp]) = \Ftot - \overline{F_{\rm{rad, ad}}} = \Ftot - k \grad_{\rm{ad}}.
\label{eqn:fconv_pz}
\end{equation}
At this point it is useful to define the radiative gradient, $\grad_{\rm{rad}} = \Ftot/k$.
Within the penetrative region, $\grad_{\rm{ad}} > \grad_{\rm{rad}}$, so Eqn.~\ref{eqn:fconv_pz} requires $\overline{\Fconv} < 0$.
Following \citet{zahn1991}, we next assume that the velocity and horizontal temperature fluctuations are highly correlated and specified by a function $h(x,y)$,
\begin{equation}
w(x,y,z) = W(z)h(x,y),
\qquad
T'(x,y,z) = \delta T(z)h(x,y).
\end{equation}
The incompressibility constraint (Eqn.~\ref{eqn:incompressible}) specifies $\overline{w} = 0$, so $\overline{h} = 0$.
However, nonlinear interactions do not disappear when horizontally averaged, so $\overline{h^2} \neq 0$.
A vertically-varying formulation of the mean convective flux follows from this formulation,
\begin{equation}
\overline{\Fconv} \equiv \overline{w T} = \overline{h^2} \, W(z) \, \delta T(z).
\label{eqn:Fconv_vertical}
\end{equation}
In the penetrative region, since $\Fconv < 0$, $W(z)$ and $\delta T(z)$ must have opposite signs; the buoyancy force will therefore decelerate penetrative flows.
In a stationary state, the penetrative zone is thus described by a balance between advection and buoyancy in the vertical momentum equation (Eqn.~\ref{eqn:momentum} with Eqn.~\ref{eqn:boussinesq}), 
\begin{equation}
\frac{1}{2}\frac{d w^2}{dz} \sim |\alpha| g T'.
\end{equation}
Multiplying both sides by $h(x,y)$, horizontally averaging, and then eliminating $\delta T(z)$ using Eqn.~\ref{eqn:Fconv_vertical}, we retrieve a simple ordinary differential equation describing convective dynamics,
\begin{equation}
\frac{\overline{h^3}}{6 |\alpha| g \overline{h^2}} dW^3 \sim \overline{\Fconv} dz.
\label{eqn:theory_ode}
\end{equation}
While we have derived this expression in the penetrative zone, it should be equally valid in a stationary convection zone; there, however, $\overline{\Fconv} > 0$.
This equation can be integrated over the depth of the convection zone (from $W = 0$ at $z = 0$ to $W = W_0$ at $z = L_s$), as well as over the penetration zone (from $W = W_0$ at $z = L_s$ to $W = 0$ at $z = L_s + \delp$).
We assume however that the horizontal structure $h$ of the flux-carrying flows is not identical in the convection zone (CZ) and the penetration zone (PZ).
Taking the ratio of these two integrals of Eqn.~\ref{eqn:theory_ode}, we find
\begin{equation}
\mD \equiv \frac{(\overline{h^3}/\overline{h^2})_{\rm{PZ}}}{(\overline{h^3}/\overline{h^2})_{\rm{CZ}}},\qquad\qquad
\frac{\int_{\rm{PZ}} \overline{\Fconv} dz}{\int_{\rm{CZ}} \overline{\Fconv} dz} = - \mD.
\label{eqn:theory_fraction}
\end{equation}
This equation represents the central result of \citet{zahn1991}'s theory: the ratio of the vertically integrated convective fluxes in the PZ and CZ is directly linked to some constant which is determined by the structure of the dynamics ($\mD$).

Eqn.~\ref{eqn:theory_fraction} is however not intuitively satisfying.
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work: a discontinuous jump in $\overline{\Fconv}$ at the convective boundary, and continuous piecewise-linear profile of $\overline{\Fconv}$ whose derivative may be discontinuous at the convective boundary.
In both of these cases, we will define a nondimensional ``Penetration Parameter,''
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)},
\label{eqn:theory_P_defn}
\end{equation}
which is the negative ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary (assuming the region above the boundary is an adiabatic penetrative zone).

\subsection{Case I: Discontinuous flux}
\label{sec:discontinuous_theory}
We first consider a model which satisfies
\begin{equation}
\overline{\Fconv}(z) = \Fcz \begin{cases}
1			&	z \leq \Lcz,\\
-\mP_D^{-1}  & 	z > \Lcz 
\end{cases}.
\end{equation}
Here, $\Fcz$ is a (constant) value of flux carried in the convection zone and $\mP_D^{-1}$ is the penetration parameter (subscript D for discontinuous case).
Plugging this functional form of the flux into Eqn.~\ref{eqn:theory_fraction}, and integrating the convection zone from $z = 0$ to $z = L_p$ and the penetration zone from $z = L_p$ to $z = L_p + \delp$,
\begin{equation}
\frac{\delp}{L_s} = \mP_D \mD.
\label{eqn:discontinuous_prediction}
\end{equation}
We see that the size of the penetration region is linearly proportional to $\mP_D$ and is a function of the structure of the convective dynamics ($\mD$).
Intuitively, this result makes sense: as $\mP_D$ grows, the magnitude of $\overline{\Fconv}$ and the breaking force of buoyancy in the PZ shrink, resulting in larger penetrative regions.

\subsection{Case II: Piecewise linear flux}
\label{sec:linear_theory}
We next assume that $\overline{\Fconv}(z)$ is not discontinuous at the CZ-PZ boundary, but that its derivative may be,
\begin{equation}
\overline{\Fconv}(z) = 
\frac{\partial \Frad}{\partial z}\bigg|_{\rm{cz}}
\begin{cases}
(L_p - z) & z \leq L_p \\
-\mP_L^{-1} (z - L_p) & z > L_p
\end{cases},
\end{equation}
where $(\partial \Frad / \partial z)|_{\rm{cz}}$ is a constant and $\mP_L$ is the penetration parameter (subscript L for linear case).
Again, solving Eqn.~\ref{eqn:theory_fraction} with this functional form of the flux, we retrieve
\begin{equation}
\frac{\delp}{L_p} = \sqrt{\mP_L \mD},
\label{eqn:linear_prediction}
\end{equation}
which is identical to the prediction of \citet{zahn1991} when we take $\mP_L = 1$.
In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
Our aim is to see if the predicted scalings with the penetration parameter $\mP$ are realized in direct numerical simulations, and to measure preliminary values for $\mD$ in local simulations.

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-defined convection zone ($L_s$), the timescale of freefall across that convection zone ($\tau_{\rm{ff}}$), and the temperature scale of the internal heating over that freefall time ($\Delta T$),
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{\alpha g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(\alpha g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain contains at least two convection zone length scales according to the Schwarzschild criterion.
We decompose the temperature field into a background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

@@

In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency $f_{\rm{conv}} \approx \angles{\vec{u}} \Lcz \approx 1$.
We want to allow the stiffness of the radiative-convective interface to be a control parameter.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}} \approx N^2,
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$, so by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.

The crucial place in which our model differs from that of prior work is that we define a ``penetration parameter,'' $\mP$, according to Eqn.~\ref{eqn:theory_P_defn}.
We construct our experiments so that $\mP$ and $\mS$ can be varied separately.
We suspect that many past experiments have implicitly set $\mP \approx \mS^{-1}$.

Aside form $\mS$ and $\mP$, the two remaining control parameters that control our experiments determine the degree of turbulence.
The value of $\mR$ roughly corresponds to the value of the peak Reynolds number $\rm{Re} = \mR |\vec{u}|$ measured in the simulations, and we set the ratio of the diffusivities $\Pran = 0.5$ throughout this work.
Astrophysical convection is in the limit of $\Pran \ll 1$ \citep{garaud2021}; we choose a modest value of $\Pran$ which slightly separates the scales between thermal and viscous structures while still allowing us to achieve convection with large Reynolds and P\'{e}clet numbers.

\subsection{Case I: Discontinuous flux}
Most of the simulations in this paper study simulations with a discontinuous convective flux at the Schwarzschild convective boundary.
We achieve this by constructing a discontinuous radiative conductivity,
\begin{equation}
k_D(z) = \begin{cases}
k_{\rm{CZ}}	&	z < 1 \\
k_{\rm{RZ}} &	z \geq 1
\end{cases}.
\label{eqn:sim_discontinuous_k}
\end{equation}
Leaving $\mS$ and $\mP_D$ as free parameters and requiring that the adiabatic gradient can carry the $\Fbot$ at $z = 0$ and that the radiative gradient can carry the flux for $z \geq 1$ specifies this system fully,
\begin{equation}
k_{\rm{RZ}} = \frac{\delta_H}{\mS\mP_D},\qquad
k_{\rm{CZ}} = k_{\rm{RZ}}\frac{1}{1 + \zeta + \mP_D^{-1}},\qquad
\gradad = Q_{\rm{mag}}\mS\mP_D(1 + \zeta + \mP_D^{-1}),\qquad
\gradrad = \gradad - Q_{\rm{mag}}\mS.
\end{equation}

@@

\subsection{Case II: Piecewise linear flux}
We additionally study a select few simulations where the flux's gradient may be discontinuous at the Schwarzschild convective boundary.
We achieve this by constructing a radiative conductivity with a piecewise discontinuous gradient,
\begin{equation}
\partial_z k = \partial_z k_0
\begin{cases}
1	&	z < 1 \\
\mP_L^{-1} &	z \geq 1
\end{cases}
\label{eqn:sim_linear_k}
\end{equation}
Since $k$ varies with height, the value of $\mS$ and $\mP$ also vary with height; we specify their values at $z = 2$.
by this choice, we require
\begin{equation}
\partial_z k_0 = \frac{\delta_H}{\Lcz \mS \xi},\qquad
k_b = \frac{\delta_H\zeta}{\mS\xi},\qquad
\gradad = Q \mS \xi,
\end{equation}
where $\xi \equiv 1 + \mP_L(1 + \zeta)$.
In these simulations, we hold $\mS = 10^3$ and $\mR = 800$ while varying $\mP_L$.
As in section \ref{sec:linear_theory}, we expect $\delta_p \propto \mP_L^{1/2}$.

@@

One additional complication is that stellar fluid dynamics exist in the regime of Pr$\,\ll1$ \citep{garaud2021}.
Dynamics in this regime may be different from those in the regime of Pr$\lesssim 1$ that we studied here, which could affect flow morphologies and thus penetration depths.
Recently, \citet{kapyla2021} found that convective flows exhibited exhibited more overshoot at low Pr than high Pr.
Future work should aim to understand how strongly the (TODO: symbol for h integrals) fraction depends on Pr.
